---
title: "HCC1395_20p_dilution_analysis"
author: "Stephanie Georges"
editor: source
format: html
embed-resources: true
editor_options: 
  chunk_output_type: console
---

## Concordance of Allele Frequencies between Diluted and Full-Strength, RUFUS-adjudicated validated SeqC2 HCC1395 SNVs

Load libaries
```{r}
library(tidyverse)
library(ggpmisc)
```


### 10% vs 100%

Load intersected txt
```{r}
data <- read.table("data/1-4/alt_snv_LL_EA_NC_tumor_20p_diluted_normal_intersect.txt", header=T)
```


Get rid of LL_EA_NC columns
```{r}
dilution_data <- data |> select(-Pos_LL_EA_NC, -Ref_LL_EA_NC, -Alt_LL_EA_NC, -DP_LL_EA_NC, -AD_LL_EA_NC)
```


Get rid of any lines that do not report the variant in both 100% and 20%
```{r}
dilution_data <- dilution_data |> filter(Pos_100 != 0 & Pos_20 != 0)
```


Filter any lines where DP is <150 or >300 (for 100 or dilution) 
```{r}
dilution_data <- dilution_data |> filter(DP_100 >= 150 & DP_100 <= 300 & DP_20 >= 150 & DP_20 <= 300)
```


Extract AD[1] value for 100% dilution sample
```{r}
dilution_data <- dilution_data |> mutate(AD_100_copy = AD_100)
dilution_data <- dilution_data |> 
  separate(AD_100_copy, into = c("AD_100_0", "AD_100_1", "AD_100_2", "AD_100_3"), sep = ",")
```


Add a column for AF[1] for 100% dilution
```{r}
dilution_data <- dilution_data |> mutate(AF_100_1 = as.numeric(AD_100_1)/as.numeric(DP_100))
```


Filter by AF > 0.2 in 100% dilution
[Note this took things from 16,423 to 12,715 (-3708 variants)]
```{r}
dilution_data <- dilution_data |> filter(AF_100_1 >= 0.20)
```


Extract AD[1] value for 20% dilution sample
```{r}
dilution_data <- dilution_data |> mutate(AD_20_copy = AD_20)
dilution_data <- dilution_data |> 
  separate(AD_20_copy, into = c("AD_20_0", "AD_20_1", "AD_20_2", "AD_20_3"), sep = ",")
```


Add a column for AF[1] for 20% dilution
```{r}
dilution_data <- dilution_data |> mutate(AF_20_1 = as.numeric(AD_20_1)/as.numeric(DP_20))
```

Determine R^2 value
```{r}

```



Plot regression line
```{r}
dilution_data |>
  ggplot(aes(x = AF_100_1, y = AF_20_1)) +
  geom_point(color="blue") + 
  labs(x = "Allele Frequency for 100% Tumor Sample", 
       y = "Allele Frequency for 20% Tumor Sample", 
       title = "Allele Frequency Concordance of 20% Tumor vs 100% Tumor",
       subtitle = "For RUFUS-adjudicated, SEQC2-validated HCC1395 SNVs") + 
  theme(plot.title = element_text(size=14)) +
  expand_limits(x = 0, y = 0) +
  stat_poly_line(color="black") + 
  stat_poly_eq()
```


